%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Pratyush - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/Pratyushdas/Pratyush-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{Pratyush-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratyush}{Singh}{ \urlstyle{same}\sectionsep \\
\href{mailto:singhpratyush551@gmail.com}{Email :- 
 singhpratyush551@gmail.com} \sectionsep \\
\href{tel:+91}{Phone No. :- }}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Vishwakarma-University VU}
\descript{BTech}
\location{July 2023 | Pune, India}
\sectionsep

\subsection{BHIS Malad}
\descript{12th | CBSE}
\location{May 2019 | Mumbai, India}
\sectionsep

\subsection{SSA Mira Road}
\descript{10th | CBSE}
\location{July 2017 | Mumbai, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 

Github:// \href{https://github.com/PratyushSingh1}{\bf pratyushsingh} \\
LinkedIn://  \href{https://www.linkedin.com/in/pratyush-singh-dataanalyst/}{\bf pratyushsingh} \\
Facebook:// \href{https://www.facebook.com/pratyush.singh.5872?mibextid=LQQJ4d}{\bf pratyushsingh} \\
Instagram:// \href{https://instagram.com/pratshhh?igshid=OGQ5ZDc2ODk2ZA==}{\bf pratyushsingh}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{Skills}
\subsection{Programming}
Python \textbullet{}   MySQL \textbullet{} Microsoft Excel \textbullet{} Power BI \textbullet{} Data Mining \textbullet{}  \\ Machine Learning \textbullet{} RDBMS\\ Web Scrapping \\ 
\sectionsep
% \location{Over 1000 lines:}
%  C++ \textbullet{} C Sharp \\
%  \sectionsep
\location{Familiar:}
Tableau \textbullet{} SAP \textbullet{} AWS
\sectionsep

\subsection{Other}
GitHub \textbullet{}   webflow \textbullet{} Vs Studio \textbullet{} Postman \\
Photoshop \textbullet{} Canva \textbullet{} Communication Skills  \textbullet{} Problem Solving \textbullet{} Leadership \\ 
Research \textbullet{} Business accumen \\
\\
\section{Certifications}
The Data Science-Udemy \textbullet{} Machine Leanring-Udemy \textbullet{} Text Anlalytics-LinkedIn Leanring \textbullet{} Power BI-Great Learning \textbullet{} Data Mining-Great Leanring  \textbullet{} Google Analytics-LinkedIn Learning \textbullet{} Social Media Marketing-LinkedIn Learning \\ 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\location{Total Experience - 1 Year }
\sectionsep
\runsubsection{W3Services Infotech India}
\descript{| Jr. Data Scientist Intern }
\location{July 2022 - May 2023 | Thane, India}
\location{(Internship)}
\vspace{\topsep}
\begin{tightemize}
\item contributed in the development of website "Lead management system" with the full stac developer team.
\item Analyzed and visualized Sales data using Power BI and MySQL to identify patterns and trends. 
\item Cleaned and manipulated data using Pandas to prepare it for Data analysis and Visualisation.
\item Performed EDA(Exploratory Data Analysis) on various projects. 
\item Managed Dashboard as well as Reporting and presentation.
\end{tightemize}
\sectionsep





\runsubsection{The spark Foundation}
\descript{| Data Science and business Analytics}
\location{February 2022 – March 2022 | Singapore, India}
\location{(Internship)}
\begin{tightemize}
\item Did Prediction using Supervised Machine Learning.
\item Did Prediction using Unsupervised ML.
\item Performed Prediction Using Decision Tree Algorithm.
\item Created a Dashboard which detects the sales and Profit of the product by country and City .
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Secure-Your-Visa (Job Board)}
\descript{| Full Stack Based Project}
\location{February 2023 – Present}
Checkout \textbf{\href{https://github.com/PratyushSingh1}{GitHub}} 
\sectionsep

\runsubsection{Netflix EDA(Exploratory data analysis)}
\descript{| Data Analysis Based project} Checkout 
 \textbf{\href{https://github.com/PratyushSingh1/Netflix-EDA}{On my GitHub }}.
\sectionsep

\runsubsection{Flipkart(Boat-Headphones)-Sentiment-Analysis}
\descript{| Data Science Based Project} Checkout code on 
 \textbf{\href{https://github.com/PratyushSingh1/Sentimental-Analysis-Flipkart-}{GitHub}}.
\sectionsep

\runsubsection{HR Analytics}
\descript{| HR Data Analysis Based Project} Checkout code on 
 \textbf{\href{https://github.com/PratyushSingh1/Hr-Analytics}{GitHub}}.
\sectionsep

\runsubsection{Cars Re-sale Data Analysis }
\descript{| Data Analysis Project} Checkout 
 \textbf{\href{https://github.com/PratyushSingh1/Cars_Data_Analysis}{GitHub}}.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2019	     & Second in CHESS competition on Sports Day organized by SAITM\\
% 2018	     & Won CHESS competition on Sports Day organized by SAITM\\
% 2017	     & 41th rank in MD University (BCA 3RD SEM) in Dec\\
% 2017	     & 49th rank in MD University (BCA 2ND SEM) in May\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
